The Weakly Nonlinear Magnetorotational Instability in a Global, Cylindrical Taylor-Couette Flow

### 2017-03-24 paper/thingap_ref_response/thingap_mri_paper_ref_response_apj.tex
last edits

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{thingap_stressfig_Pm_1E-2}
\caption{\edit1{Total (Reynolds + Maxwell) stress in the domain as predicted from the weakly nonlinear theory for \Pm=1E-2.}} \label{fig:wnl_stress}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{sim_theory_energy_jdot_Pm_1E-2_nonorm}
\caption{\edit1{Average energy (left) and angular momentum transport (right) in the total, kinetic, and magnetic components of simulation data as a function of time. Gray lines show the weakly nonlinear theory values for each quantity. }} \label{fig:sim_theory_energy_jdot}
\end{figure*}

@@

\edit1{We analyze the average energy and angular momentum transport in the simulation domain (Figure \ref{fig:sim_theory_energy_jdot}). The theory slightly overpredicts both quantities, though with a reasonably good agreement considering that the weakly nonlinear theory applies rigorously to a channel of infinite height, while the simulation was carried out in a box with a vertical extent of only two critical wavelengths. We defer further comparisons between simulation and theory, including an analysis of the effect of the box height on the simulated flow, to future work. }

%\textbf{SUSAN: SIMULATION RESULTS GO HERE}

@@

@@

>>>>

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{thingap_stressfig_Pm_1E-2}
\caption{\edit1{Total (Reynolds + Maxwell) stress in the domain as predicted from the weakly nonlinear theory for $\Pm=1E-2$.}} \label{fig:wnl_stress}
\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{sim_theory_energy_jdot_Pm_1E-2_Bmaxnorm}
\caption{\edit1{Average energy (left) and angular momentum transport (right) in the total, kinetic, and magnetic components of simulation data as a function of time. Gray lines show the weakly nonlinear theory values for each quantity. }} \label{fig:sim_theory_energy_jdot}
\end{figure*}

@@

\edit1{We analyze the average energy and angular momentum transport in the simulation domain (Figure \ref{fig:sim_theory_energy_jdot}). The saturation amplitude predicted by the weakly nonlinear theory depends on the choice of normalization of the linear eigenvectors. The eigenvectors of the linear problem are only determined up to an arbitrary normalization, and the nonlinear coefficient of the Ginzburg-Landau equation is sensitive to this normalization. The undetermined factor is typically assigned by comparison with direct numerical simulation or laboratory experiment \citep[e.g.][]{Deyirmenjian:1997,Recktenwald:1993}. Here we determine the constant by requiring that the maximum amplitude of $B_y$ be equal in both theory and simulation. With this normalization choice all plotted quantities agree to within $\sim 25\%$. The theory and simulation are thus in reasonably good agreement considering that the weakly nonlinear theory applies rigorously to a channel of infinite height, while the simulation was carried out in a box with a vertical extent of only two critical wavelengths. We defer further comparisons between simulation and theory, including an analysis of the effect of the box height on the simulated flow, to future work.  }

@@

\bibitem[{Deyirmenjian(1997)}]{Deyirmenjian:1997}
Deyirmenjian, Z., Daya, A., \& Morris, S.W., 1997, Phys. Rev. E 56, 1706

@@

\bibitem[{Recktenwald et al.(1993)}]{Recktenwald:1993}
Recktenwald, A., L\"ucke, M., M\"uller, H.W., 1993, PhRvE 48, 4444

### 2017-03-24 paper/widegap_ref_response/widegap_mri_paper_ref_response_apj.tex
last edits

We solve the equations at each order using Dedalus, an open source pseudospectral code. We solve the radial portion of the eigenvectors on a basis of Chebyshev polynomials subject to our radial boundary conditions. \edit1{We use a 512-component Chebyshev grid, and confirm numerical convergence at $1.5\times$ the resolution. Because }
We solve Equation \ref{eq:ordere} as a linear eigenvalue problem, and Equation \ref{eq:ordere2} as a linear boundary value problem. 
The result of the weakly nonlinear analysis is a single amplitude equation for $\alpha$. This amplitude equation is found by enforcing a solvability condition on Equation \ref{eq:ordere3}. We find

>>>>

We solve the equations at each order using Dedalus, an open source pseudospectral code. We solve the radial portion of the eigenvectors on a basis of Chebyshev polynomials subject to our radial boundary conditions. \edit1{We use a 512-component Chebyshev grid, and confirm numerical convergence at $1.5\times$ the resolution. This is sufficient to determine convergence because of the faster-than-exponential convergence of spectral methods. }
We solve Equation \ref{eq:ordere} as a linear eigenvalue problem, and Equation \ref{eq:ordere2} as a linear boundary value problem. 
The result of the weakly nonlinear analysis is a single amplitude equation for $\alpha$. This amplitude equation is found by enforcing a solvability condition on Equation \ref{eq:ordere3}. We find
